Ecosystem size and complexity are extrinsic drivers of food chain length in branching networks

### 2022-06-02 rmd/manuscript.Rmd
edit minor

No data were used or produced in this research. R functions for simulations are provided as the R package mcbrnet version 1.2.3 (available at [<https://github.com/aterui/mcbrnet>](https://github.com/aterui/mcbrnet){.uri}). Codes for simulations, statistical analysis, figures, and tables are available at [<https://github.com/aterui/public-proj_fcl-river-theory>](https://github.com/aterui/public-proj_fcl-river-theory){.uri}.

>>>>

No data were used or produced in this research. R functions for simulations are provided as the R package mcbrnet version 1.2.3 (available at [\<https://github.com/aterui/mcbrnet\>](https://github.com/aterui/mcbrnet){.uri}). Codes for simulations, statistical analysis, figures, and tables are available at [\<https://github.com/aterui/public-proj_fcl-river-theory\>](https://github.com/aterui/public-proj_fcl-river-theory){.uri}.
